\chapter{Conclusion and Future Scope}

\section{Conclusion}
In conclusion, the development of the Airbnb clone full stack application has been successfully completed. The project aimed to replicate the core functionalities and user experience of the original Airbnb website. By utilizing modern technologies such as NextJS, TypeScript, Prisma, TailwindCSS, MongoDB, and Cloudinary, a responsive and feature-rich application was implemented.

Throughout the project, various key objectives were achieved. The user interface and user experience closely match that of the original Airbnb website, providing a familiar and intuitive platform for users to list and rent properties. The use of NextJS and intelligent rendering techniques ensured optimal performance and a seamless browsing experience. Integration with NextAuth enabled users to sign up and authenticate using email credentials or their existing Google or Github accounts.

The project also followed industry-standard coding practices, incorporating ESLint and TypeScript to enforce coding standards and maintain code quality. The database schema design adhered to best practices, ensuring efficient data storage and retrieval.

Overall, the Airbnb clone project has demonstrated the ability to develop a functional and responsive full stack application that replicates the core features of the original Airbnb website.

\section{Future Scope}
While the project has met the defined objectives, there are several areas that can be further enhanced and expanded in the future:

\begin{enumerate}
	\item \textbf{User Reviews and Ratings: } Implementing a user review and rating system would enhance the trust and credibility of the platform. Users can leave reviews and ratings for properties they have rented, providing valuable feedback to both hosts and potential renters.
	\item \textbf{Messaging System: } Introducing a messaging system between hosts and guests would facilitate communication and streamline the booking process. 
	\item \textbf{Payment Integration: } Integrating a secure and reliable payment gateway would allow users to make online payments for property reservations. This would provide a seamless booking experience and ensure secure transactions.
	\item \textbf{Mobile Application: } Developing a mobile application for the Airbnb clone would extend the reach and accessibility of the platform, allowing users to access and interact with the application on their mobile devices.
	\item \textbf{Localization and Internationalization: }Implementing localization and internationalization features would enable the application to support multiple languages and currencies, catering to a global user base.
\end{enumerate}

In conclusion, the Airbnb clone project has laid a solid foundation for a fully functional and user-friendly platform. With the potential future enhancements mentioned above, the application can be further improved to meet the evolving needs of users and provide a comprehensive solution for property rental services.