\chapter{Introduction}

In today's digital age, the online marketplace for short-term accommodations has experienced significant growth. Platforms like Airbnb have revolutionized the way people find and rent properties, providing a convenient and personalized experience. The purpose of this project is to develop a full stack application that replicates the core functionality and user experience of Airbnb, catering to the increasing demand for such platforms.

The current available solutions for property rentals often lack the flexibility, customization, and seamless user experience that users desire. While there are existing platforms like Airbnb that offer a wide range of properties for rent, they may not fully cater to specific user preferences or provide a user interface that closely matches the original website. This project aims to bridge these gaps by offering a functional clone of Airbnb that closely mimics its features, design, and user experience.

The significance of this project lies in its ability to provide a comprehensive solution for property rentals, offering users a platform that matches the familiarity and functionality of Airbnb. By developing a full stack application, we can address the limitations of current solutions and provide users with a more tailored experience. The project's focus on responsive design, advanced filtering options, and integration of popular web development technologies ensures an enhanced user experience and improved efficiency for both property owners and renters.

This report will provide an overview of the project's objectives, the technologies employed, and the database design. We will discuss the implementation details, including the utilization of NextJS, Typescript, Prisma, TailwindCSS, MongoDB, and Cloudinary. Additionally, we will delve into the integration of NextAuth for secure user authentication and social login options. The report will also highlight the significance of this project in meeting the current market demands and address the gaps present in existing solutions.

By the end of this report, readers will have a clear understanding of the development process, the technologies utilized, and the overall contribution of this project to the field of online property rentals.