\chapter*{\centering ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT} 

This report presents the development and implementation of a full stack application that serves as a functional clone of the popular website Airbnb. The application allows users to list their properties for rent, make reservations for accommodations, and provides various filtering options based on location, room count, bathroom count, and guest count. The project utilizes modern web development technologies, including NextJS, Typescript, Prisma, TailwindCSS, MongoDB, and Cloudinary. The application employs both server-side and client-side rendering for optimal performance. Additionally, NextAuth is integrated to provide users with authentication options, including traditional email and password credentials as well as social login using Google or GitHub accounts.

In this project, we have successfully developed a full stack application that closely replicates the core functionality and user experience of Airbnb. The application offers users the ability to list their properties for rent and make reservations for accommodations, all while providing a user-friendly interface that matches the design of the original Airbnb website. By leveraging NextJS, Typescript, Prisma, TailwindCSS, MongoDB, and Cloudinary, we have ensured a robust and scalable application that meets the demands of a real-world marketplace. The use of server-side and client-side rendering techniques enhances performance, while NextAuth enables secure authentication with multiple login options. This project demonstrates proficiency in web development technologies, database design, and UI/UX implementation.

\textbf{Keywords:} full stack application, Airbnb clone, NextJS, Typescript, Prisma, TailwindCSS, MongoDB, Cloudinary, server-side rendering, client-side rendering, NextAuth, authentication, UI/UX design, database design.